Medical Concept Extraction

### 2012-12-16 paper/paper.tex
Changing a TODO(SAM) -> TODO(TJN)
Updating data use agreement subsection.

Such dearth of training data means that the amount of test data is often much larger than the amount of training data available. Consequently, it is even more difficult to obtain decent results if the models trained even moderately overfit the training data.

\subsection{Data Usage Agreements}
TODO(SAM):

>>>>

Such dearth of training data means that the amount of test data is often much larger than the amount of training data available. Consequently, it is even more difficult to obtain decent results if the models trained even moderately overfit the training data -- a particular risk due to the sparse distribution of high dimensional items discussed previously.

\subsection{Data Usage Agreements}
In addition to limited availability of data, it is often difficult to obtain the data that is relevant. Even for ``open'' data sets such as those provided by the i2b2 National Center for Biomedical Computing, one must sign a data use agreement in order to maintain compliance with the U.S. Health Insurance and Accountability Act (HIPAA) privacy and security rules. The approval process for ``open'' data sets can still take weeks, while access to more controlled data sets can often take months and require security measures such as single physical machine access.
